\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-04 coqimpl.tex
Add code for Section 5.1
resolve comments

\subsection{Language Design}\YZ{I think in §3.1, you should use a figure to show how the actual code the programmer will write to solve the programming challenge outlined in Figure 1.}\EDJreply{Done.}
Inspired by the above challenges and Family Polymorphism, we propose
the following extension to Coq's Vernacular Commands, and the corresponding STLC example.
% basically write down the specification of surface Coq commandline
%   and then explain  how the language design makes the programmer’s life easier
\begin{align*}
  V := \quad &"Family"~\langle ident\rangle~["extends"~\langle ident\rangle] 
  \quad |\quad "EndFamily" \\
  & |\quad "FRecursor"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle~"using"~\langle ident\rangle \\
  & | \quad "FTheorem"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle \\
  & |\quad "Extend"~"Family"~\langle ident\rangle \\ 
  & |\quad ["Extend"]~"FInductive"~\langle ident\rangle \\ 
  & |\quad ["Final" | "Override"]~"Field"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\
  & | \quad "FieldClaim"~\langle ident\rangle~":"~\langle term \rangle \\
  & | \quad "Inherit"~\langle ident\rangle \quad | \quad "Inherit Until"~\langle ident\rangle \quad | \quad ...
\end{align*}

@@

Though inheritance is solely a first-order data rather
than a ``mapping'', it is still possible to
\text{mix-in} two inheritance data---by carefully ``mix'' the internal list, we can compose the inheritance. However, a good definition of mixin is still under investigation. We will show one practical example of \textit{mixin} later.\YZ{How about making mixin composition one of your Req's? Also does any example in the paper illustrate how to do this?}\EDJreply{mixin is not really formalized. There is no example illustrate it. The only example is the STLC example at the very end and I just kind of ``mention'' it. I think here I just want to emphasize, inheritance as first order data is still possible to support composition.}

>>>>

\subsection{Language Design}

Inspired by the above challenges and Family Polymorphism, we propose
the following extension to Coq's Vernacular Commands, and the corresponding STLC example.
% basically write down the specification of surface Coq commandline
%   and then explain  how the language design makes the programmer’s life easier
\begin{align*}
  V := \quad &"Family"~\langle ident\rangle~["extends"~\langle ident\rangle] 
  \quad |\quad "EndFamily" \\
  & |\quad "FRecursor"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle~"using"~\langle ident\rangle \\
  & | \quad "FTheorem"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle \\
  & |\quad "Extend"~"Family"~\langle ident\rangle \\ 
  & |\quad ["Extend"]~"FInductive"~\langle ident\rangle \\ 
  & |\quad ["Final" | "Override"]~"Field"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\
  & | \quad "FieldClaim"~\langle ident\rangle~":"~\langle term \rangle \\
  & | \quad "Inherit"~\langle ident\rangle \quad | \quad "Inherit Until"~\langle ident\rangle \quad | \quad ...
\end{align*}

@@

Though inheritance is solely a first-order data rather
than a ``mapping'', it is still possible to
\text{mixin} two inheritance data---by carefully ``mix'' the internal list, we can compose the inheritance. However, a good definition of mixin is still under investigation. We will show one practical example of \textit{mixin} later.\YZ{How about making mixin composition one of your Req's? Also does any example in the paper illustrate how to do this?}\EDJreply{mixin is not really formalized. There is no example illustrate it. The only example is the STLC example at the very end and I just kind of ``mention'' it. I think here I just want to emphasize, inheritance as first order data is still possible to support composition.}

### 2022-07-04 lang-design.tex
resolve comments

% we want to be able to reason pattern matching as well
% However, there is still difference between data recursion and induction
% reasoning, because the former one is \textit{proof-relevant}. This
% difference leads to another issue: \textlabel{Req (4)}{chg:definition-relevant-reasoning}:
% \textbf{we need to reason about (the computation about) extensible
% pattern matching}, just like "subst_lemma" in \cref{fig:STLC-example}.
% When proving "subst_lemma", we have to know "subst" is invariant on
% "tt", i.e., \mintinline{Coq}{(subst i x tt) = tt}. This kind of
% information requires exposing \textit{computational rules} from the
% recursors.
\YZ{Seems like what's missing here is to
convince the reader why exposing the definition of subst could be a
problem for family polymorphism.}\EDJreply{Actually I don't see why I need to emphasize this "as a problem". This is just a requirement like any other requirements earlier. I don't know how to show its difficulty at this early stage.}\YZreply{There is apparently a tension between the need to expose definitional equality and the ability to override. Looking at the bigger picture, I think this section reads better if phrased as discussing challenges posed by adding family polymorphism to a proof assistant. I have some initial ideas that I need to discuss with you.}\EDJreply{Design Space section is rewritten into Challenge now.}

>>>>

% we want to be able to reason pattern matching as well
% However, there is still difference between data recursion and induction
% reasoning, because the former one is \textit{proof-relevant}. This
% difference leads to another issue: \textlabel{Req (4)}{chg:definition-relevant-reasoning}:
% \textbf{we need to reason about (the computation about) extensible
% pattern matching}, just like "subst_lemma" in \cref{fig:STLC-example}.
% When proving "subst_lemma", we have to know "subst" is invariant on
% "tt", i.e., \mintinline{Coq}{(subst i x tt) = tt}. This kind of
% information requires exposing \textit{computational rules} from the
% recursors.
